The DAO Hack

### 2019-01-06 paper/paper.tex
added some information about what
linebreak after dot
fixed grammer and flow issues

\documentclass[a4paper, 11pt]{scrartcl}

@@

The blockchain is a sequence of interlocked blocks of data. Those block essentialy contain the link to a parent block and a ennumeration of transactions. They are generated by the ethereum network and as such, nobody is in control of the blockchain itself. Decisions have to be made by the majority of the network or else the network would split into two different sub-chains. \cite{blockchainKai}

@@

The Blockchain can be split at all times. Meaning everybody can take the chain and create a new block for any older parent block. Mostly smaller splits are simply ignored because they are non-consequential. However, when a larger part of the network decides that they want to change something, they could take the blockchain as it was at any point in time and create a new chain which has it's own history and it's own cryptocurrency. \cite{blockchainKai}

@@

The validation of a signature is not the only usecase for smart contracts. A transaction could be bound to an arbitary amount of rules that can be represented by the scripting language. \cite{blockchainKai}

@@

Ethereum is one type of a cryptocurrency. Its main difference to others like Bitcoin is that it can run a complex programming language called Solidity. With Solidity you can create loops, functions and recursion which then are run on the ethereum blockchain. This has huge advantages as one can create powerful smart contracts and bind the payment to those. Only with such a powerful language the DAO could be created. \cite{eth}

@@

\section{How was that possible?}

>>>>

%!TEX program = lualatex
\documentclass[a4paper, 11pt]{scrartcl}

@@

The blockchain is a sequence of interlocked blocks of data.
Those block essentially contain the link to a parent block and an enumeration of transactions.
They are generated by the ethereum network and as such, nobody is in control of the blockchain itself.
Decisions have to be made by the majority of the network or else the network would split into two different sub-chains. \cite{blockchainKai}

@@

The Blockchain can be split at all times.
Meaning everybody can take the chain and create a new block for any older parent block.
Mostly smaller splits are simply ignored because they are non-consequential.
However, when a larger part of the network decides that they want to change something, they could take the blockchain as it was at any point in time and create a new chain which has its own history and its own cryptocurrency. \cite{blockchainKai}

@@

The validation of a signature is not the only use case for smart contracts.
A transaction could be bound to an arbitrary amount of rules that can be represented by the scripting language. \cite{blockchainKai}

@@

Ethereum is one type of cryptocurrency.
Its main difference to others like Bitcoin is that it can run a complex programming language called Solidity.
With Solidity, you can create loops, functions and recursion which then are run on the ethereum blockchain.
This has huge advantages as one can create powerful smart contracts and bind the payment to those.
Only with such a powerful language the DAO could be created. \cite{eth}

@@

In May 2016 when the DAO was launched on the ethereum blockchain it was funded with 12.7M ether.
As one ether was worth about 10-12 Dollars at that time, this corresponds to about 150 million dollars.

Soon after, on June 18, 2016, an unknown party was able to drain the funds of the DAO by exploiting a security bug that was present in the function that is used to withdraw the ether.
He was able to retrieve 3.5M ether which at that times would have been around 45 million dollars.

\subsection{How was that possible?}

The DAO includes the functionality to split the DAO.
This was intended for people who either want to retrieve their funds or who weren't happy with the decisions of the DAO and wanted to invest differently.
Everybody could split the DAO at any time with a one-week waiting period.

The split function has on
